%% Master CV - Muhammad Idris
%% Comprehensive overview of all competencies, experience, and achievements.
%% Use as a master reference when tailoring role-specific CVs (cv/main_<company>.tex).
%%
%% Compile with: lualatex main_example.tex
%% (pdflatex often fails on modern MiKTeX with fontawesome5 font-expansion errors.)

\documentclass[11pt,a4paper,sans]{moderncv}
\moderncvstyle{banking}
\moderncvcolor{blue}

% Force both first and last name AND section headings to render in moderncv
% blue (color1). Default banking on lualatex+MiKTeX leaves these black, which
% looks inconsistent with the rest of the blue accent scheme.
\renewcommand*{\firstnamestyle}[1]{{\fontsize{34}{36}\bfseries\upshape\color{color1}#1}}
\renewcommand*{\lastnamestyle}[1]{{\fontsize{34}{36}\bfseries\upshape\color{color1}#1}}
\renewcommand*{\sectionstyle}[1]{{\sectionfont\color{color1}#1}}

\usepackage[utf8]{inputenc}
\usepackage{needspace}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,
    urlcolor=blue,
    pdftitle={Muhammad Idris - CV},
    pdfpagemode=FullScreen,
}
\usepackage[scale=0.80]{geometry}
\usepackage{import}

% personal data
\name{Muhammad}{Idris}
\address{Germany}{}{}
\phone[mobile]{+49 162 2613711}
\email{mi.muhammad@outlook.com}
\extrainfo{\href{https://www.linkedin.com/in/muhammad-muhammad-idris/}{LinkedIn}, \href{https://github.com/sabhack}{GitHub}}

\begin{document}

\makecvtitle

% ============================================================
%     PROFILE STATEMENT
% ============================================================

\vspace{6pt}
\small{Mechatronics \& Robotics engineer (M.Eng., DAAD scholar) specializing in autonomous mobile robots. Built and validated a radar-inertial control architecture for an AMR on slippery warehouse floors --- from FMCW-radar/IMU sensing and ROS~2 control to a SolidWorks-to-URDF digital twin and full SIL/HIL validation. Strong in C++/Python, control systems, and sensor fusion, with end-to-end experience taking robots from concept to working hardware. Seeking a robotics / mechatronics engineering role in Germany.}

% ============================================================
%     CORE COMPETENCIES
% ============================================================

\section{Core Competencies}
\vspace{1pt}
\begin{itemize}

\item \textbf{Robotics \& Middleware}: ROS~2 (Ubuntu 24.04), AMR/AGV, differential-drive kinematics, robotic-arm manipulation, intralogistics robotics.

\item \textbf{Control Systems}: Interval Type-2 Fuzzy Logic (IT2-FLC), PID, robust control; motor control (FOC, BLDC, VESC 6 MK VI) over CAN bus.

\item \textbf{Perception \& Sensor Fusion}: FMCW radar (SICK RMS2000), ToF sensors, Luxonis OAK-D, magnetic encoders, SLAM, odometry, real-time signal processing.

\item \textbf{Programming}: C++ (primary), Python, MATLAB/Simulink; embedded Linux, Git.

\item \textbf{Simulation \& Test}: Digital twin, Gazebo, RViz2, URDF/XACRO, SolidWorks/CAD; V-Model, SIL/HIL testing.

\end{itemize}

% ============================================================
%     PROFESSIONAL EXPERIENCE
% ============================================================

\section{Professional Experience}
\vspace{3pt}
\begin{itemize}

\needspace{5\baselineskip}
\item{\cventry{2024--2026}{Student Research Intern --- Mechatronics \& Robotics Lab}{Hochschule Schmalkalden}{Schmalkalden, Germany}{}{\vspace{1pt}
\begin{itemize}
    \item Developed and validated a radar-inertial slip-mitigation architecture on a custom-built 2WD differential-drive AMR using FMCW radar and magnetic encoders; reduced trajectory drift under all tested slip conditions.
    \item Implemented an Interval Type-2 Fuzzy Logic Controller in a ROS~2 framework, integrating VESC~6 MK~VI motor controllers via CAN bus for real-time torque correction.
    \item Built a high-fidelity digital twin in SolidWorks, exported to URDF, and validated the full control stack in Gazebo + RViz2 using SIL and HIL methodologies.
    \item Implemented real-time Doppler ground-velocity signal processing (median + EMA filtering); achieved stable slip-ratio estimation independent of floor friction.
\end{itemize}}}

\vspace{3pt}

\needspace{5\baselineskip}
\item{\cventry{2020--2024}{Graduate Teaching Assistant --- Mechatronics Engineering}{Air Force Institute of Technology (AFIT)}{Kaduna, Nigeria}{}{\vspace{1pt}
\begin{itemize}
    \item Designed and delivered laboratory exercises on automation principles, mobile-robot navigation, and sensor integration for undergraduate cohorts.
    \item Mentored students on control-systems implementation and embedded programming in C++/Linux; supported research on autonomous navigation and multi-sensor fusion.
\end{itemize}}}

\vspace{3pt}

\needspace{5\baselineskip}
\item{\cventry{2016--2018}{Junior Software Engineer --- Engineering Department}{Sensotronica Limited}{Minsk, Belarus}{}{\vspace{1pt}
\begin{itemize}
    \item Developed web-based and augmented-reality operator interfaces for industrial monitoring systems.
    \item Implemented performance-optimized C++ software on Linux; reduced system response latency through architectural refactoring.
\end{itemize}}}

\end{itemize}

% ============================================================
%     EDUCATION
% ============================================================

\section{Education}
\vspace{1pt}
\begin{itemize}

\needspace{4\baselineskip}
\item{\cventry{2024--2026}{M.Eng. Mechatronics, Robotics \& Automation Engineering}{Hochschule Schmalkalden}{Germany}{}{\vspace{1pt}
Thesis: ``Radar-Inertial Robust Control for Autonomous Mobile Robots: Mitigating Trajectory Drift on Slippery Warehouse Floors.'' DAAD scholarship holder.
}}

\vspace{3pt}

\item{\cventry{2013--2018}{B.Eng. Mechatronics, Robotics \& Automation Engineering}{Belarusian National Technical University (BNTU)}{Minsk, Belarus}{}{\vspace{1pt}
Graduated with High Honors. Thesis: real-time monitoring dashboard for hydrogen-generator control (JavaScript / microservices).
}}

\end{itemize}

% ============================================================
%     LANGUAGES
% ============================================================

\section{Languages}
\vspace{1pt}
\begin{itemize}
\item English (C1, fluent), German (B2, targeting C1), Russian (B2, intermediate).
\end{itemize}

% ============================================================
%     HONORS AND AWARDS
% ============================================================

\section{Honors and Awards}
\vspace{1pt}
\begin{itemize}
\item{\textbf{DAAD-Stipendium} --- full Master's-study scholarship, Deutscher Akademischer Austauschdienst (2024--2026).}
\end{itemize}

% ============================================================
%     REFERENCES
% ============================================================

\section{References}
\vspace{1pt}
\begin{itemize}
\item{Available upon request.}
\end{itemize}

\end{document}
